\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

% resume starts here
\begin{document}

% name
\centerline{\Huge Evan Xu}

\vspace{5pt}

% contact information
\centerline{\href{mailto:xuevanj@gmail.com}{xuevanj@gmail.com} | (978)-836-3470 | \href{Linkedin.com/in/EvxnXu}{Linkedin.com/in/EvxnXu} | \href{github.com/EvxnXu}{github.com/EvxnXu}}

\vspace{-10pt}

% education section
\section*{Education}
\textbf{University of Massachusetts at Lowell} -- BS in Computer Science\hfill Expected: December 2025

\textbf{GPA:} 3.80 \newline \newline
\textbf{Relevant Coursework as of Spring 2025:} Object-Oriented Programming, Data Structures, Assembly, Algorithms, AI, Machine Learning, Linear Algebra, Calculus, Probability \\


\vspace{-9pt}

% skills section
\section*{Skills}
\textbf{Languages:} C, C++, C\#, Java, Python, SQL, SQLite\\
\textbf{Tools:} Git, Team Foundation Source Control, Swagger, Visual Studio, VSCode

\vspace{-9pt}

% experience section
\section*{Experience}

\textbf{Program Development Intern}  \hfill June 2024 -- August 2024 \\
\href{https://www.salary.com/}{Salary.com} -- Waltham, MA \\
\vspace{-9pt}
\begin{itemize}
  \item Developed an .NET Core Web API to import data from excel spreadsheets into a SQL Database.
  \item  Implemented search solution for newsletter web pages using Apache Lucene.NET and Windows Forms.
\end{itemize}

\textbf{Grading Assistant for the Department of Mathematics} \hfill September 2024 -- Current \\
University of Massachusetts at Lowell -- Lowell, MA \\
\vspace{-9pt}
\begin{itemize}
    \item Communicated quickly and efficiently to deliver quality, consistent, and punctual results in a timely fashion.
    \item Accurately diagnosed areas for improvement in student work and provided accurate feedback.
\end{itemize}
\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Poker Bankroll Application} | Java, JavaFX, SQLite \hfill August 2024\\
\vspace{-9pt}
\begin{itemize}
    \item Implemented a Desktop Application to track bankroll value over time using a SQLite database.
    \item Designed a UI using JavaFX to allow user to retrieve visual representation of data from the database and import data to database.
\end{itemize}

\textbf{Sokoban Game} | C++\hfill April 2024\\
\vspace{-9pt}
\begin{itemize}
  \item Created a game known as Sokoban in which the player controls a character on a grid with the goal of pushing one or more boxes into a target space.
  \item Implemented logic to restrict object movement in accordance with object collision, and restrict player movement upon achieving victory.
  \item Added undo feature that allowed player to undo their last action until reaching the start of the level.
\end{itemize}

\textbf{Random Text Generator} | C++ \hfill March 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item  Designed a program that uses text input to generate a Markov Model.
  \item Produced probability based text of varying precision based on a generated Markov Model.
\end{itemize}

\textbf{N-Body Simulation} | C++ \hfill January 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Created a graphical representation of a Universe using the SFML library.
  \item Implemented logic for celestial bodies movement resulting from changes in velocity from gravitation forces.
\end{itemize}

\textbf{Portfolio Website} | HTML/CSS \hfill March 2022 \\
\vspace{-9pt}
\begin{itemize}
    \item Designed a portfolio web page hosted on Github pages with features like drop-down menus, size-scaling for different resolution, etc.

\end{itemize}
% alternate formatting for projects section
% \section*{Projects}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}

\vspace{-18.5pt}


\end{document}
